How to compute the fusion product of MV cycles in type A

### 2021-02-21 draft.tex
graff typo missed a Kinf
should have brackets around star product in circ construction right

    We also have a lattice descriptions 
    % {\small
    \begin{gather*}
    \Grbd = 
    \{ L \subset  \CC(t)^m, s \in \CC : \text{ $L$ is a $\CC[t]$-lattice 
    % , $L$ is 
    trivial at any $ a \ne 0, s$} \} \\
     \Gr_{0,s} = 
    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
    \end{gather*}%}
    \acom{$s\in\CC$ should be $s\in\AA$?}
    \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
    % 
    \item The positive parts $ \Gr^+$ and ${\Grth}^+$ of the affine Grassmannian and of the thick affine Grassmannian resp.\ are defined as 
    % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
    $$
    \Gr^+ = (M_m(\cO) \cap G(\cK)) / G(\cO) \quad {\Grth}^+ = (M_m(\CC[t]) \cap G(\CC\xT[t^{-1}]) / G(\CC[t]) 
    $$
    % \acom{What is $M_m$?} \jcom{The space of matrices.  I added it to the beginning of section 2.}

@@

We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.  
We use the projection $ \pi: \Grbd \rightarrow \AA $ to form $ X_1 \circ X_2 = X_1 \ast_\AA X_2 \cap \pi^{-1}(0) = \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
We regard $ X_1 \circ X_2$ as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. 
% \acom{Repeat question: what is this iso? Roger says maybe it's in MV?}
% \jcom{Now answered above.}

>>>>

    We also have a lattice descriptions 
    % {\small
    \begin{gather*}
    \Grbd = 
    \{ L \subset  \CC(t)^m, s \in \CC : \text{ $L$ is a $\CC[t]$-lattice 
    % , $L$ is 
    trivial at any $ a \ne 0, s$} \} \\
     \Gr_{0,s} = 
    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
    \end{gather*}%}
    \acom{$s\in\CC$ should be $s\in\AA$?}
    \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
    % 
    \item The positive parts $ \Gr^+$ and ${\Grth}^+$ of the affine Grassmannian and of the thick affine Grassmannian resp.\ are defined as 
    % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
    $$
    \Gr^+ = (M_m(\cO) \cap G(\cK)) / G(\cO) \quad {\Grth}^+ = (M_m(\CC[t]) \cap G(\Kinf) / G(\CC[t]) % \CC\xT[t^{-1}] missed a spot  
    $$
    % \acom{What is $M_m$?} \jcom{The space of matrices.  I added it to the beginning of section 2.}

@@

We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.  
We use the projection $ \pi: \Grbd \rightarrow \AA $ to form $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) = \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
We regard $ X_1 \circ X_2$ as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. 
% \acom{Repeat question: what is this iso? Roger says maybe it's in MV?}
% \jcom{Now answered above.}
